Dynamics of Laterally Propagating Flames in X-ray Bursts. II. Realistic Burning \& Rotation

### 2020-12-23 xrb2/paper.tex
higher resolution phase plots

The mean molecular weight $\bar{A}$ within each of our simulations seems to grow along defined tracks confined to certain temperatures $T$, as shown in the Figure \ref{fig:abar} phase plots. We believe that the tracks in the plot correspond to reaction pathways in the reaction network. Comparing Figure \ref{fig:abar} to \citet{flame_wave1}, these tracks are much more neat and clearly defined. The ''messiness" of the tracks may be dependent on how mixed the flame interior is --- since these new simulations are un-boosted, they may be inherently less mixed than those in \citet{flame_wave1}. {\tt F1000} aligns with this interpretation: its $\bar{A}$ tracks are somewhat disrupted compared to the slower rotation runs, possibly due to the more vigorous mixing of the vortex at the flame front. Comparing the different runs, we also see that as the rotation rate increases, so does the peak temperature. This makes sense if higher rotation leads to a more concentrated, intense vortex near the flame front. It also agrees with our earlier interpretation of the enhanced burning seen in Figure \ref{fig:time_series_1000} for {\tt F1000}. The disruption of reaction pathways with higher rotation rates and mixed flames may have interesting consequences; if the reactions are disrupted enough, it is possible that the burning could be snuffed out. This can occur in combustion scenarios when the turbulent vortices become so small they penetrate the reaction zone and completely disrupt the burning.

\begin{figure}[t]
    \centering
    \plotone{urho_plot_0_1}{}
    \caption{\label{fig:urho}Phase plot of the horizontal $x$-velocity $u$, density $\rho$ and the nuclear energy generation rate $\dot{e}_{\rm nuc}$ for the 250, 500 and 1000~Hz runs. The slightly lower $\dot{e}_{\rm nuc}$ values along the $u = 0$ axis are most likely a numerical artifact related to the density gradient setup and finite resolution of these simulations.}
\end{figure}

\begin{figure}[t]
    \centering
    \plotone{uv_plot_0_1}
    \caption{\label{fig:uv}Phase plot of the horizontal $x$-velocity $u$, vertical $y$-velocity $v$ and the nuclear energy generation rate $\dot{e}_{\rm nuc}$ for the 250, 500 and 1000~Hz runs.}
\end{figure}

\begin{figure}[t]
    \centering
    \plotone{abar_plot_0_1}
    \caption{\label{fig:abar}Phase plot of the mean molecular weight $\bar{A}$, temperature $T$ and the nuclear energy generation rate $\dot{e}_{\rm nuc}$ for the 250, 500 and 1000~Hz runs.}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \plotone{abar_plot_hotter}
    \caption{\label{fig:abar_hot}Phase plot of the mean molecular weight $\bar{A}$, temperature $T$ and the nuclear energy generation rate $\dot{e}_{\rm nuc}$ for the 500~Hz runs with $T_{\rm star}$ of $10^8$~K, $2\times10^8$~K and $3\times10^8$~K.}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \plotone{urho_plot_hotter}
    \caption{\label{fig:urho_hot}Phase plot of the horizontal $x$-velocity $u$, density $\rho$ and the nuclear energy generation rate $\dot{e}_{\rm nuc}$ for the 500~Hz runs with $T_{\rm star}$ of $10^8$~K, $2\times10^8$~K and $3\times10^8$~K.}
\end{figure}

\begin{figure}[t]
    \centering
    \plotone{uv_plot_hotter}
    \caption{\label{fig:uv_hot}Phase plot of the horizontal $x$-velocity $u$, vertical $y$-velocity $v$ and the nuclear energy generation rate $\dot{e}_{\rm nuc}$ for the 500~Hz runs with $T_{\rm star}$ of $10^8$~K, $2\times10^8$~K and $3\times10^8$~K.}
\end{figure}

>>>>

The mean molecular weight $\bar{A}$ within each of our simulations seems to grow along defined tracks confined to certain temperatures $T$, as shown in the Figure \ref{fig:abar} phase plots. We believe that the tracks in the plot correspond to reaction pathways in the reaction network. Comparing Figure \ref{fig:abar} to \citet{flame_wave1}, these tracks are much more neat and clearly defined. The ''messiness" of the tracks may be dependent on how mixed the flame interior is. Since these new simulations are un-boosted, they may be inherently less mixed than those in \citet{flame_wave1}. {\tt F1000} aligns with this interpretation: its $\bar{A}$ tracks are somewhat disrupted compared to the slower rotation runs, possibly due to the more vigorous mixing of the vortex at the flame front. Comparing the different runs, we also see that as the rotation rate increases, so does the peak temperature. This makes sense if higher rotation leads to a more concentrated, intense vortex near the flame front. It also agrees with our earlier interpretation of the enhanced burning seen in Figure \ref{fig:time_series_1000} for {\tt F1000}. The disruption of reaction pathways with higher rotation rates and mixed flames may have interesting consequences; if the reactions are disrupted enough, it is possible that the burning could be snuffed out. This can occur in combustion scenarios when the turbulent vortices become so small they penetrate the reaction zone and completely disrupt the burning.

\begin{figure}[t]
    \centering
    \plotone{urho_plot_0_1}{}
    \caption{\label{fig:urho}Phase plot of the horizontal $x$-velocity $u$, density $\rho$ and the nuclear energy generation rate $\dot{e}_{\rm nuc}$ for the 250, 500 and 1000~Hz runs at $t = 100$~ms. The slightly lower $\dot{e}_{\rm nuc}$ values along the $u = 0$ axis are most likely a numerical artifact related to the density gradient setup and finite resolution of these simulations.}
\end{figure}

\begin{figure}[t]
    \centering
    \plotone{uv_plot_0_1}
    \caption{\label{fig:uv}Phase plot of the horizontal $x$-velocity $u$, vertical $y$-velocity $v$ and the nuclear energy generation rate $\dot{e}_{\rm nuc}$ for the 250, 500 and 1000~Hz runs at $t = 100$~ms.}
\end{figure}

\begin{figure}[t]
    \centering
    \plotone{abar_plot_0_1}
    \caption{\label{fig:abar}Phase plot of the mean molecular weight $\bar{A}$, temperature $T$ and the nuclear energy generation rate $\dot{e}_{\rm nuc}$ for the 250, 500 and 1000~Hz runs at $t = 100$~ms.}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \plotone{abar_plot_hotter}
    \caption{\label{fig:abar_hot}Phase plot of the mean molecular weight $\bar{A}$, temperature $T$ and the nuclear energy generation rate $\dot{e}_{\rm nuc}$ for the 500~Hz runs with $T_{\rm star}$ of $10^8$~K, $2\times10^8$~K and $3\times10^8$~K at $t = 40$~ms.}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \plotone{urho_plot_hotter}
    \caption{\label{fig:urho_hot}Phase plot of the horizontal $x$-velocity $u$, density $\rho$ and the nuclear energy generation rate $\dot{e}_{\rm nuc}$ for the 500~Hz runs with $T_{\rm star}$ of $10^8$~K, $2\times10^8$~K and $3\times10^8$~K at $t = 40$~ms.}
\end{figure}

\begin{figure}[t]
    \centering
    \plotone{uv_plot_hotter}
    \caption{\label{fig:uv_hot}Phase plot of the horizontal $x$-velocity $u$, vertical $y$-velocity $v$ and the nuclear energy generation rate $\dot{e}_{\rm nuc}$ for the 500~Hz runs with $T_{\rm star}$ of $10^8$~K, $2\times10^8$~K and $3\times10^8$~K at $t = 40$~ms.}
\end{figure}
